---
title: "Mercury Pressure App"
author: "William MacKay"
date: "2/7/2019"
output: ioslides_presentation
---

## Application Overview

This is a rather simple application that takes a tempature input from the user and predicts the vapor pressure using a polynomial regression. 

All the user has to do is select the desired temperature with the slider in the side panel. 

The vapor pressure prediction is displayed in text and on a plot in main panel. 

## The Data

The data used to make this prediction is the "pressure" data from the R package **Datasets**

```{r data, echo = TRUE}
library(datasets)
head(pressure)

```

## Main Features of the Application

- Temperature Select Slider
- Prediction Display (text and plot)
- Polynomial Prediction Model

## The Prediction Model

```{r model, echo=FALSE}
# Avoid object error
temperature <- pressure$temperature

# Build model
model <- lm(pressure ~ poly(temperature, 10, raw = TRUE), data = pressure)

```

This model leverages polynomials due to the exponential nature of the dataset. A purely linear model would produce inaccurate results. 

## Example

If the user were to select 300 as the temperature, the model would produce this answer: 

```{r example, warning=FALSE}
result <- predict(model, newdata = data.frame(temperature = 300))
result
```


## Thank you!

See the app here: (https://wmackay.shinyapps.io/Mercury_Pressure_App) 
